Evolutionary Quantum Transition (EQT): A Novel Solution to Optimization Problems \\

### 2020-09-30 paper_nit.tex
draft3

\title{Evolved Quantum Computing Based Problem Solving\\
% {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
% should not be used}
% \thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

\begin{abstract}
Quantum Computing (QC) has often been touted as an esoteric and terrifying field of computing research. However, the possible advantages offered by the inherent quantum fundamentals beseeches extensive additional ventures into this field. Just as QP offers exciting ideas in the field of computing, Genetic Programming (GP) offers an application oriented optimization route. GP uses Darwinian theories to maintain a set of candidate solutions, apply multiple operations on the candidates and eventually declare a global winner. In this paper, we combine QC and a flavour of GP to create a new interdisciplinary front of computational intelligence. 
\end{abstract}

@@

Majority of the problems faced in any aspect of computer science, in one way or another, involves a catch-22 of multi-functional optimization. Entire fields have been dedicated to solving a generic version of this issue. The most common method of dealing with optimization problems is to be in collaboration with another interdisciplinary frontier acting in the capacity of a helper function.

\subsection{Computing Methodologies}

Most form of computational algorithms in the present day, are executed on a conventional computer. The fundamental notation used for differentiating Classical Computing (CC) and QC \cite{nara} is the basic unit of information. While classical computers use bits 0 and 1, quantum computers use "one of" two computational basis states. The label awarded to these states is "bra-ket" notation i.e, state $\ket{0}$ or $\ket{1}$. Bits are assigned states 0 or 1 deterministically and independently. However, qbuits can exist in a superposition state of $\alpha\textsubscript{0}$$\ket{0}$ + $\alpha\textsubscript{1}$$\ket{1}$, where $\alpha{0}$ and $\alpha{1}$ are complex numbers, such that $|\alpha\textsubscript{0}|\textsuperscript{2}$ + $|\alpha\textsubscript{1}|\textsuperscript{2}$ = 1.

@@

The field of applied quantum mechanics is still unexplored for the best part. However, there are certain applications in which QC outperforms CC. Consider Shor's algorithm \cite{shor} and RSA \cite{rsa}, both of which are used for encryption. Basically, the encryption of any form of data transmitted over the Internet relies immensley on factorization of a huge number. This process is extremley ardous for a non-quantum computer, with the best known factoring technique requiring an amount of time proportional to 2$\textsuperscript{n\textsuperscript{\sufr{1}{3}}log(n)\textsuperscript{\sufr{2}{3}}}$ 
, where $\textit{n}$ is the number of digits in the number to be factored \cite{guo}. Meanwhile Shor's Quantum algorithm requires time proportional to only $n\textsuperscript{2}log(n)log(log(n))$ \cite{ham}.

QC takes advantage of major quantum phenomena such as superposition, quantum entanglment, principle of uncertainity among others \cite{az}, for improving existing searchc and optimization techniques. Humans inherently stick to definitive physical concepts such as deterministic state transition, state duality and temporal static behaviour of particles.

According to Moore's Law, the size of computational units shrinks at an exponential rate as the number of transistors on a chipset increases every year. Even after accounting for physical constraints, a time will come when operations will be conducted on an atomic scale. On such a level, atomic forces overpower particle physics naturally. As a result, understanding QC and applying them in a virtual landscape to get a sense of their possibilities is a must.

@@

Evolutionary Algorithms (EA) \cite{vik} encompass a wide array of research ideas stemming from general principles of genetics and the theory of evolution. Models are developed to illustrate the behaviour of naturally occuring phenomena, develop these algorithms and test out the application of the corresponding theory. The general process of any EA is depicted in figure \ref{p1}. In a nutshell, an initial population of candidate solutions is generated and each solution is labelled according to their performance on a set fitness function. Further down the line, these candidates are improved upon by conducting a set of operations on them for a predetermined number of generations. After some stopping criterias are achieved, the process strops and the best candidate is hypothesized as the global solution. The advantages offered by this technqiue include but not limited to resilience to noise, in-built support for parallelism and distributed learning, multi-pronged attack and handling complex problems.

@@

Our paper provides an insight into the ensemble of both the previously mentioned techniques and preparing algorithms for a future where quantum computers replace traditional computers as commonplace machines.

\section{Methodology}

One of the most famous quantum effect invovles "superposition" \cite{rj}, which allows a quantum entity to exist simultaneously. As a result memory conservation capabilities of any quantum system increases exponentially. Coupling this idea with multiple evolutionary aspects, we present a novel computational frontier.

\subsection{Existing Convention}

Consider the following problem; Assume the position of a process $\textit{P}$ in a finite state system of $\textit{n}$ states at time $\textit{t}$ to be $\textit{x\textsubscript{i}}$. Create a general procedure to reach position $\textit{x\textsubscript{j}}$ at time $\textit{t+1}$.

The conventional process would involve declaration of a register of size $\textit{n}$ and listing out all possible combinations for reaching state $\textit{x\textsubscript{j}}$ along with the costs. This would be followed by creation of a logical circutry of gates mapping the input state to the output state using boolean primitives. The entire process could still be automated using certain advanced algorithms. However, the memory utilization will not be optimal as all possible state transitions must be considered before building the circuit. Figure $\ref{p2}$ displays the state table, state diagram and accompanying circuit diagram for a D flip flop. Notice that all possible states for the input have been mentioned in the state table. This constitues a huge waste of memory as majority of the inputs are never encountered and some states could be invalid. QC aims to reduce this inefficiency between making all the states dependent on each other.

\begin{figure}[!b]
\centering\includegraphics[width=8cm]{ss.jpg}
\caption{States for D flip flop}
\label{p2}
\end{figure}

\subsection{Applied Quantum Mechanics}
Classicial state transitions cannot fathom superposition and hence will always be fixated on one fixed state. For the D flip flop example, the number of inputs are two and hence the number of output states is $2\textsuperscript{2}$ for each starting state. The 4 possible states can be represented as an one-hot encoded vector with each bit representing the state of the output. For example, the vector shown below represents state 00 for an input state of 0.
$$
\begin{bmatrix} 
1&0&0&0\\
\end{bmatrix}
\quad
$$

@@

Evolved self-organizing computer programs utilize the techniques described in the previous section to solve problems. In this paper the following general problem structure is considered; How to design a circuit to travel from state $\textit{A}$ to state $\textit{B}$? These problem types are called "Oracle Analysis" as they require we to determine some property of a valid quantum gate with no prior information on the intermediate states and what combination of gates results in what output. Some of the key terminologies used in the following texts are explained in Table $\ref{tab:1}$

\subsection{Problem Solving Technique}

\subsection{Key Points}
Some of the important points governing the flow of the algorithm are mentioned below:

@@

\subsection{Fitness Selection}
The evolutionary algorithm depends greatly on the quality of the fitness function. It forms the basis for the next generation. In CC, tailor-made fitness function might suffice for each problem. But for a self-organizing QC system, the main program would have to run multiple times to determine the fitness from each output. Even if a real quantum computer was used, we would get one output and it's associated probability from each epoch. The probability of error so obtained could then be utilized to function as a fitness function. The only drawback in this method would be the absense of a quantum computer and the result exponential computational resources.

@@

\subsection{Schema Theorem}
The Schema Theorem \cite{st} dictates which chromosomes move on through the selection phase. If we consider each chromosome as a binary string, there are three possibilities for each bit. It can either be a 1, or a 0 or a * (wildcard) value. The wildcard bit can have either a 1 or a 0. There are two defining characteristics which dictate the goodness of fit.

@@

Due to the unavailability of a quantum computer, an artificial environment was created and simulations were conducted in it. The experiment was set up on a 64-bit Machine with Ubuntu 20.04, Intel® CoreTM i5-7200U CPU @ 2.50GHz × 4, with a GeForce 940MX/PCle/SSE2 graphic card.

In order to design a quantum state system, we provide the program with a set of input qubits mapped to set of ouput qubit. As discussed previously the fitness function is chosen as a lexicographic combination of the number of misses and probability of error as given in Equation $\ref{eq:5}$, where $\alpha$ is a scaling factor, $\textit{m}$ is number of misses and $\textit{e}$ is probability of error. Lower the value returned by the fitness function, higher is the solution's quality.
{\scriptsize
\begin{equation}
\label{eq:5}
f = \alpha m + e
\end{equation}
}%
Following this, an initial set of chromosomes corresponding to the ideal circuit were created and gently evolved for set number of generations. The generation progression is composed of the previously mentioned genetic operators. A global count of the best fitness achieved for far is mentioned and the matrix corresponding to that score is declared as the optimal circuit design. The results have been composed for 100 generations in 10 test runs and displayed in Table $\ref{tab:1}$.

>>>>

\title{Evolutionary Quantum Transition (EQT): A Novel Solution to Optimization Problems \\
% {\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
% should not be used}
% \thanks{Identify applicable funding agency here. If none, delete this.}
}

@@

\begin{abstract}
Quantum Computing (QC) has often been touted as an esoteric and terrifying field of computing research. However, the possible advantages offered by the inherent quantum fundamentals beseeches extensive additional ventures into this field. Likewise, Evolutionary Computing (EC) offers a multi-pronged approach by deploying several candidates into the search space with constraints guiding the search process. In this paper, we present Evolutionary Quantum Transition to provide a unique solution to a flavour to optimization solving processes using concepts borrowed from QC and EC. The combination leverages compute power to explore the space of candidate solutions by introducing smarter techniques. The solution so obtained provides the optimal transition solution with an automated circuit selection process which can be attributed to the amazing capabilites of QC and EC. 
\end{abstract}

@@

Majority of the problems faced in any aspect of computer science, in one way or another, involves a catch-22 of functional optimization. Entire fields have been dedicated to solving a generic version of this issue. The most common method of dealing with optimization problems is to be in collaboration with another interdisciplinary frontier acting in the capacity of a helper function.

\subsection{Modeling an Optimization Problem}
Before any optimization can be performed, a mathematical or computational model for the problem must be prepared \cite{hara}. The quality of the model is just as crucial to the optimization task as the techniques employed. Drafting the model requires explicitly stating the variables, constraints and objective functions involved followed by selection of an appropriate algorithm for the search process.

\subsection{Problem Formalization}
The optimzation problems considered in this paper belong to the family of Multi-Objective Optimization Problems (MOOPs)\cite{mul}. Any other problem format can be derived from this main branch. A general MOOP is defined in Equation :

{\scriptsize
\begin{equation}
Optimize \{f\textsubscript{1}(x), f\textsubscript{2}(x), \dots, f\textsubscript{k}(x)\}
\end{equation}
}

where $f\textsubscript{i}(x)$ is the $i\textsuperscript{th}$ sub-problem subject to certain constraints. The decision vector $X$ = ($x\textsubscript{1}, x\textsubscript{2}, \dots, x\textsubscript{n}$) belong to a nonempty feasible region $S$. The objective solution vector $Z$ =  $(f\textsubscript{1}(x), f\textsubscript{2}(x), \dots, f\textsubscript{k}(x))$ represents the required mapping in the feasible objective region $Z$.

Such a mapping is considered to be optimal if none of the individual components can be improved without degradation of at least one other component and such a solution vector is called a Pareto optimal solution \cite{pare}. An ideal objective vector $z\textsuperscript{*}$ can be obatined by minimizing every objective function individually subject to $S$. A vector strictly better than $z\textsuperscript{*}$ is called a utopian objective vector $z\textsuperscript{**}$. Similarly the upper bounds of the Pareto Optimal set constitute a nadir objective vector $z\textsuperscript{nad}$. Once the variables are decided, we can embark upon finding a solution to the optimization problem. There are various techniques which can be chosen to solve the problem. The most popular ones are desribed in the next section.

\section{Computing Methologies}

Once the problem statement is defined and the model is formulated, a computing technique must be selected for solving the MOOP. Historically, three main verticals have stood out as prime candidates for solving MOOPs. They been described in Table $\ref{tab:1}$.

\begin{table*}[!t]
\caption{\textsc{Computing Methodologies}}
\label{tab:1}
\centering
{
\begin{tabular}{| c | c | c | c |}
\hline
\textbf{Method} & \textbf{Key Points} & \textbf{Advantages} & \textbf{Disadvantages} \\
\hline
& Use of bits for information & Intuative, Can be modelled at & High space complexity, susceptible\\
Classical Computing (CC)&transmission, Deterministic Modeling, &present, Easier state transition,& to noise, Limited parallelism,\\
&Used to day-to-day tasks& Resources are available on-the-go & Slow convergence rate\\
\hline
& Multiple search candidates, & Faster convergence to solution, & Computationally Intensive \\
Evolutionary Computing (EC)& Concepts borrowed from nature,& Independent of complexity of problem,& Sensitive to parameter tuning,\\
&Easily understandable&Mathematical representation optional& Optimal solution not guarenteed\\
\hline
& Use of Quantum mechanics, & Rapid solution search, & Quantum Mechincial knowledge as \\
Quantum Computing (QC)& Bra-ket representation instead of bits, & Space conservation, & a prerequisite, Not Intuative, \\
&Stochastic Modeling&Unprecedented Computational abilities&Lack of Quantum resources\\
\hline
\end{tabular}
}
\end{table*}

@@

% The field of applied quantum mechanics is still unexplored for the best part. However, there are certain applications in which QC outperforms CC. Consider Shor's algorithm \cite{shor} and RSA \cite{rsa}, both of which are used for encryption. Basically, the encryption of any form of data transmitted over the Internet relies immensley on factorization of a huge number. This process is extremley ardous for a non-quantum computer, with the best known factoring technique requiring an amount of time proportional to 2$\textsuperscript{n\textsuperscript{\sufr{1}{3}}log(n)\textsuperscript{\sufr{2}{3}}}$ 
% , where $\textit{n}$ is the number of digits in the number to be factored \cite{guo}. Meanwhile Shor's Quantum algorithm requires time proportional to only $n\textsuperscript{2}log(n)log(log(n))$ \cite{ham}.

EQT utilizes major quantum phenomena such as superposition, quantum entanglment, principle of uncertainity among others \cite{az}, for improving existing search and optimization techniques. Moreover, the space saving capabilities offered by QC are excellent additions to EQT.  The time required for processing a search request decreases exponentially in a QC environment as multiple states are entangled.  
% according to Moore's Law the size of computational units shrinks at an exponential rate as the number of transistors on a chipset increases every year. Even after accounting for physical constraints, a time will come when operations will be conducted on an atomic scale which quantum physics dominates classical physics. As a result, understanding QC and applying them in a virtual landscape to get a sense of their possibilities is a must.

@@

Evolutionary Algorithms (EA) \cite{vik} encompass a wide array of research ideas stemming from general principles of genetics and the theory of evolution. Models are developed to illustrate the behaviour of naturally occuring phenomena, develop these algorithms and test out the application of the corresponding theory. The general process of any EA is depicted in figure \ref{p1}. Borrowing this concept EQT generates an initial population of candidate solutionsand each solution is labelled according to their performance on a set fitness function until a stopping criteria is met. The dominating solution, so obtained, corresponds to the global solution

@@

\subsection{A Novel Ensemble}
As we have seen, each vertical offers it's own advantages and disadvantages when it comes to solving an optimization problem. A trade-off exists between CC and QC when it comes to delivering quality results in a reduced time frame and availability of resources to implement the search process. Meanwhile, EC offers a multi-pronged approach to the search process by applying certain constraints and operators which results in the emergence of the best results with a decreased time complexity. EQT borrows the most promising concepts from QC and EC to provide a new front to solving optimization problems. The general MOOP is a relatively broad set of problems, with each individual problem requiring certain tweaks to the solution search process. In this paper, we narrow down the MOOPs to a specific case i.e, Design a circuit to achieve state $j$ from $i$ with multiple cost considerations. 
% \subsection{Computing Methodologies}
% 
% Most form of computational algorithms in the present day, are executed on a conventional computer. The fundamental notation used for differentiating Classical Computing (CC) and QC \cite{nara} is the basic unit of information. While classical computers use bits 0 and 1, quantum computers use "one of" two computational basis states. The label awarded to these states is "bra-ket" notation i.e, state $\ket{0}$ or $\ket{1}$. Bits are assigned states 0 or 1 deterministically and independently. However, qbuits can exist in a superposition state of $\alpha\textsubscript{0}$$\ket{0}$ + $\alpha\textsubscript{1}$$\ket{1}$, where $\alpha{0}$ and $\alpha{1}$ are complex numbers, such that $|\alpha\textsubscript{0}|\textsuperscript{2}$ + $|\alpha\textsubscript{1}|\textsuperscript{2}$ = 1.
%

% \section{Methodology}
% 
% Our paper provides an insight into the ensemble of both the previously mentioned techniques and preparing algorithms for a future where quantum computers replace traditional computers as commonplace machines. 
% \subsection{Existing Convention}
% 
% Consider the previously stated problem; Assume the position of a process $\textit{P}$ in a finite state system of $\textit{n}$ states at time $\textit{t}$ to be $\textit{x\textsubscript{i}}$. Create a general procedure to reach position $\textit{x\textsubscript{j}}$ at time $\textit{t+1}$.
% 
% The conventional process would involve declaration of a register of size $\textit{n}$ and listing out all possible combinations for reaching state $\textit{x\textsubscript{j}}$ along with the costs. This would be followed by creation of a logical circutry of gates mapping the input state to the output state using boolean primitives. The entire process could still be automated using certain advanced algorithms. However, the memory utilization will not be optimal as all possible state transitions must be considered before building the circuit. Figure $\ref{p2}$ displays the state table, state diagram and accompanying circuit diagram for a D flip flop. Notice that all possible states for the input have been mentioned in the state table. This constitues a huge waste of memory as majority of the inputs are never encountered and some states could be invalid. QC aims to reduce this inefficiency between making all the states dependent on each other. 
% 
\begin{figure}[!b]
\centering\includegraphics[width=8cm]{ss.jpg}
\caption{States for D flip flop}
\label{p2}
\end{figure}
% 
% \subsection{Applied Quantum Mechanics}
% Classicial state transitions cannot fathom superposition and hence will always be fixated on one fixed state. For the D flip flop example, the number of inputs are two and hence the number of output states is $2\textsuperscript{2}$ for each starting state. The 4 possible states can be represented as an one-hot encoded vector with each bit representing the state of the output. For example, the vector shown below represents state 00 for an input state of 0.
% $$
% \begin{bmatrix} 
% 1&0&0&0\\
% \end{bmatrix}
% \quad
% $$
% 
% Quantum Mechanics is a generalized extension of classical method. The first generalization comes in the form of the temporal values of the elements of the matrix. In QC qubits are utilized instead of bits and as a result the state vectors are variables. Instead of 0 and 1, state vector can be constituted of complex numbers which meet the condition of unitarity. For any matrix $\textit{M}$ to be an unitarity matrix, the only necessary condition is shown in Equation $\ref{eq:1}$ where $M\textsuperscript{$\dagger$}$ is the Hermitean adjoint of $\textit{M}$ and $\textit{I}$ is the identity matrix. 
% {\scriptsize
% \begin{equation}
% \label{eq:1}
% M\textsuperscript{$\dagger$}M = MM\textsuperscript{$\dagger$} = I
% \end{equation}
% }
% 
% To facilitate the design of circuitry of state diagrams, QC introduces a set of gates to utilize the power of quantum mechanics \cite{qg}. The noteworthy ones are mentioned below:
% 
% \begin{itemize}
% \item QNOT: This gate is the quantum extension of the controlled NOT gate in CC. A controlled NOT gate performs the inversion operation on the right-most bit of a vector iff the left-most bit is 1. A 1-bit QNOT gate is depicted as follows:
% $$
% \begin{bmatrix} 
% 0&1\\
% 1&0\\
% \end{bmatrix}
% \quad
% $$
% \item SRN: The application of Square Root of NOT puts a qubit into a state of equal superposition through controlled randomization based on the qubit's past state. A 1-bit SRN is shown below:
% $$
% \begin{bmatrix} 
% \frac{1}{\sqrt{2}}&\frac{-1}{\sqrt{2}}\\
% \frac{1}{\sqrt{2}}&\frac{1}{\sqrt{2}}\\
% \end{bmatrix}
% \quad
% $$
% \item Swap: As the name suggests, this gate is used to swap the states of two qubits and is represented as:
% $$
% \begin{bmatrix} 
% {1}&{0}&{0}&{0}\\
% {0}&{0}&{1}&{0}\\
% {0}&{1}&{0}&{0}\\
% {0}&{0}&{0}&{1}\\
% \end{bmatrix}
% \quad
% $$
% \item Parameterized Rotation: This is a family of 1-qubit rotations parameterized by angle $\theta$ and is given by:
% $$
% \begin{bmatrix} 
% cos(\theta)&sin(\theta)\\
% -sin(\theta)&cos(\theta)\\
% \end{bmatrix}
% \quad
% $$
% \end{itemize}
% 
% \subsection{Applied Evolutionary Operators}
% 
% EA have been used extensively for complex optimization problems due to quality results even with a lack of mathematical representation, convexity and continuity. They apply a stochastic method and hence expedite the search process. However, EA are not without their flaws which include a probabilistic convergence to the global optima. 
% 
% In this paper, we follow a genetic modified Grey Wolf Optimization (GWO) algorithm \cite{gwo} to obtain and update candidate solutions. GWO follows a hierarchical structure of candidate solution which imitates the behaviour of Grey Wolves as observed in nature. The structure of $\alpha$, $\beta$, $\delta$ and $\omega$ labelled wolves. The $\alpha$ wolves are responsible for finding the global optimum whilst being guided by the $\beta$ wolves. The $\delta$ and $\omega$ provide secondary assistance to the leaders and hence maitain the dominant structure. After each search iteration, genetic operators like selection, crossover and mutation are applied to every candidate in the structure. The entire process is discribed in Algorithm $\ref{alg:gwo}$
% 
% \begin{algorithm}[t]
% \footnotesize
% \caption{GWO pseudocode}
% \label{alg:gwo}
% \begin{algorithmic}[1]
% \STATE \textbf{Input:} Population size $\textit{n}$, random vectors $\vec{r\textsubscript{1}}$, $\vec{r\textsubscript{2}} \in$ [0,1], initial prey location $\vec{D}$, number of iterations \textit{I}, fitness function $\textit{f}$, coefficient vectors $\vec{A}$, $\vec{C}$ and $\vec{a}$
% \STATE Set $\textit{t}$ = 0
% \FOR{i $\in$ [1,n]}    
% \STATE Generate wolf pack population $\textit{X\textsubscript{i}(t)}$ at instance $\textit{t}$
% \STATE Evaluate each individual against the fitness function
% \ENDFOR
% \STATE Assign $\alpha, \beta, \delta$ titles to the top three solutions
% \STATE Evaluate $\vec{D} = |\vec{C} \cdot \vec{X\textsubscript{p}}(t) - \vec{X}(t)|$
% \FOR{\textit{i} in \textit{I}}
% \FOR{Each individual in $\textit{n}$}  
% \STATE $\vec{X\textsubscript{1}} = \vec{X\textsubscript{$\alpha$}} - \vec{A\textsubscript{1}} \cdot  \vec{D\textsubscript{$\alpha$}}$
% \STATE $\vec{X\textsubscript{2}} = \vec{X\textsubscript{$\beta$}} - \vec{A\textsubscript{2}} \cdot  \vec{D\textsubscript{$\beta$}}$
% \STATE $\vec{X\textsubscript{3}} = \vec{X\textsubscript{$\delta$}} - \vec{A\textsubscript{3}} \cdot  \vec{D\textsubscript{$\delta$}}$
% \STATE Evaluate $\vec{X}(t+1) = \frac{\vec{X\textsubscript{1}} + \vec{X\textsubscript{2}} + \vec{X\textsubscript{3}}}{3}$
% \ENDFOR
% \STATE Update the coefficient vectors $\vec{A}$ and $\vec{C}$
% \STATE $\vec{A} = 2\vec{a} \cdot \vec{r\textsubscript{1}} - \vec{a}$
% \STATE $\vec{C} = 2\vec{r\textsubscript{2}}$
% \STATE Linearly decrease $\vec{a}$ from 2 to 0
% % \STATE Update $\vec{X\textsubscript{$\alpha$}}, \vec{X\textsubscript{$\beta$}}, \vec{X\textsubscript{$\delta$}}$
% \STATE Perform Crossover, Selection and Mutation
% \STATE Increment $\textit{t}$
% \ENDFOR
% \STATE $\vec{X\textsubscript{$\alpha$}}$ corresponds to the global optimum. 
% \end{algorithmic}
% \end{algorithm}
% 
% The genetic operators for a sample candidate in the form of a genomic are explained here following which the process is depicted in Figure :
% \begin{itemize}
% \item Selection: Given a population of potential solutions, selection involves grading these solutions against a fitness function. The selected solutions are cast into the crossover stage.
% \item Crossover: From the selected set of solutions, randomly two solutions are selected and the next generation chromosome is created which shares the best attributes of it's parents.
% \item Mutation: The selected solutions undergo random changes in their composition to promote diversity and increase their changes of converging to the global optimum.
% \end{itemize}
% 
% \begin{figure}[!t]
% \centering\includegraphics[width=7cm]{p2.png}
% \caption{Genetic Operators}
% \label{p3}
% \end{figure}

Evolved self-organizing computer programs \cite{self} utilize the techniques described in the previous section to solve problems. In this paper the following general problem structure is considered; How to design a circuit to travel from state $\textit{A}$ to state $\textit{B}$? These problem types are called "Oracle Analysis" as they require we to determine some property of a valid quantum gate with no prior information on the intermediate states and what combination of gates results in what output. Some of the key terminologies used in the following texts are explained in Table $\ref{tab:1}$

\subsection{Conventional Approach}
The conventional process would involve declaration of a register of size $\textit{n}$ and listing out all possible combinations for reaching state $\textit{x\textsubscript{j}}$ along with the costs. This would be followed by creation of a logical circutry of gates mapping the input state to the output state using boolean primitives. The entire process could still be automated using certain advanced algorithms. However, the memory utilization will not be optimal as all possible state transitions must be considered before building the circuit. Figure $\ref{p2}$ displays the state table, state diagram and accompanying circuit diagram for a D flip flop. Notice that all possible states for the input have been mentioned in the state table. This constitues a huge waste of memory as majority of the inputs are never encountered and some states could be invalid. QC aims to reduce this inefficiency between making all the states dependent on each other.

\subsection{Modern Approach}

The conventional approach is extremely inefficient and arduous. EQT offers an elegant solution by utilizing the best of both the worlds.

\subsubsection{Applied Quantum Mechanics}
Classicial state transitions cannot fathom superposition and hence will always be fixated on one fixed state. For the D flip flop example, the number of inputs are two and hence the number of output states is $2\textsuperscript{2}$ for each starting state. The 4 possible states can be represented as an one-hot encoded vector with each bit representing the state of the output. For example, the vector shown below represents state 00 for an input state of 0.
$$
\begin{bmatrix} 
1&0&0&0\\
\end{bmatrix}
\quad
$$

@@

As an example consider, initial state as [1 1 1 0 0 0 0 1] and the target state as [1 0 1 0 0 1 0 0]. Applying the concepts discussed previously, a quantum circuit gate is created for this transition and the associated matrix is given by 
$$
\begin{bmatrix}
\begin{bmatrix}
-0.14112954-0.16700839j& 0.07983181-0.29873381j\\
-0.25803742+0.38299128j& 0.22384403+0.01717024j\\
0.06272906+0.25203229j& -0.17352533+0.18676704j\\
-0.46040214-0.12675132j& -0.11769043+0.46751876j\\
\end{bmatrix}\\
\begin{bmatrix}
0.31172643+0.14024689j& -0.11225685-0.02087697j\\
0.16743502+0.29588733j&  0.18771276+0.01118339j\\
0.57520561+0.33055889j&  0.13856821-0.24062621j\\
0.15502007-0.07663589j& -0.38171798-0.16226323j\\
\end{bmatrix}\\
\begin{bmatrix}
0.23308965-0.15943424j& 0.26838968-0.17899447j\\
-0.19340125+0.42085285j&-0.1072532 +0.1531806j\\
0.04524549-0.44413067j& 0.15183147-0.24693186j\\
-0.2982411 +0.05650701j&  0.18590532-0.3958033j\\
\end{bmatrix}\\
\begin{bmatrix}
-0.07005404+0.04745812j& -0.27252377-0.17790739j\\
-0.2187864 +0.24156256j& -0.26294328+0.3396825j\\
0.10360916-0.35043418j&  0.12404486+0.42213862j\\
0.44304366-0.02873782j& -0.22363463+0.14806583j\\
\end{bmatrix}\\
\begin{bmatrix}
0.37175985+0.28751052j &-0.07056257-0.1013915j\\  
-0.35527493+0.07918063j & 0.48963077-0.31625964j\\
-0.20088489-0.20871619j &-0.19892169-0.09136702j\\
0.29164278+0.21288127j  &0.08750707+0.14750696j\\
\end{bmatrix}\\
\begin{bmatrix}
-0.38421248-0.04067692j& 0.16637992+0.61802823j\\ 
-0.17373866+0.27097997j& 0.18105618-0.29023612j \\
0.02505396-0.15353303j& 0.11080511+0.16151108j\\
-0.02153527+0.158645j& -0.32556212-0.16206476j\\
\end{bmatrix}\\
\begin{bmatrix}
0.19075161-0.30210472j& -0.09189932-0.2130557j\\  
-0.13117622-0.29864423j&  0.01177846-0.25807943j\\
-0.11828712+0.02111738j&  0.687924  +0.04122678j\\
-0.12997132+0.21518361j& -0.28512878+0.10722509j\\
\end{bmatrix}\\
\begin{bmatrix}
0.50059262+0.00708867j& -0.01602864+0.44984401j\\  
0.01398646+0.08782445j& -0.25293655+0.32748978j\\
-0.13217757+0.13982117j& -0.11740198+0.07269765j\\
-0.1949218 +0.44227633j& -0.09510568+0.26242716j\\
\end{bmatrix}\\

\end{bmatrix}
$$
\subsection{Key Points}
Some of the important points governing the flow of the algorithm are mentioned below:

@@

\subsection{QC Critical Factor: Schema Theorem}
The Schema Theorem \cite{st} dictates which chromosomes move on through the selection phase. If we consider each chromosome as a binary string, there are three possibilities for each bit. It can either be a 1, or a 0 or a * (wildcard) value. The wildcard bit can have either a 1 or a 0. There are two defining characteristics which dictate the goodness of fit.

\subsection{EC Critical Factor: Fitness Selection}
The evolutionary algorithm depends greatly on the quality of the fitness function \cite{haram}. It forms the basis for the next generation. In CC, tailor-made fitness function might suffice for each problem. But for a self-organizing QC system, the main program would have to run multiple times to determine the fitness from each output. Even if a real quantum computer was used, we would get one output and it's associated probability from each epoch. The probability of error so obtained could then be utilized to function as a fitness function. The only drawback in this method would be the absense of a quantum computer and the result exponential computational resources.

@@

@@

\subsection{Experimental Setup}
Due to the unavailability of a quantum computer, an artificial environment was created and simulations were conducted in it. The experiment was set up on a 64-bit Machine with Ubuntu 20.04, Intel® CoreTM i5-7200U CPU @ 2.50GHz × 4, with a GeForce 940MX/PCle/SSE2 graphic card.

In order to design a quantum state system, we provide the program with a set of input qubits mapped to set of ouput qubit. As discussed previously the fitness function is chosen as a lexicographic combination of the number of misses and probability of error as given in Equation $\ref{eq:5}$, where $\alpha$ is a scaling factor, $\textit{m}$ is number of misses and $\textit{e}$ is probability of error \cite{lex}. Lower the value returned by the fitness function, higher is the solution's quality.
{\scriptsize
\begin{equation}
\label{eq:5}
f = \alpha m + e
\end{equation}
}%

\subsection{Result}
Following this, an initial set of chromosomes corresponding to the ideal circuit were created and gently evolved for set number of generations. The generation progression is composed of the previously mentioned genetic operators. A global count of the best fitness achieved for far is mentioned and the matrix corresponding to that score is declared as the optimal circuit design \cite{cir}. The results have been composed for 100 generations in 10 test runs and displayed in Table $\ref{tab:2}$.

\begin{table*}[!t]
\caption{\textsc{Results}}
\label{tab:2}
\centering
{
\begin{tabular}{| c | c | c | c | c |}
\hline
Experiment No. & Input Qubit & Output Qubit & Number of Chromosomes &  Best Fitness Value \\
\hline
 & [0 1 1 1 0 1 0 0] & [0 0 0 0 1 1 1 1] & 10 & 0.5081 \\
1 & [0 1 1 1 0 1 0 0] & [0 0 0 0 1 1 1 1] & 50 & 0.5134 \\
 & [0 1 1 1 0 1 0 0] & [0 0 0 0 1 1 1 1] & 100 & 0.5106 \\
\hline
 & [0 1 1 0 0 1 1 1] & [0 0 1 0 1 0 1 1] & 10 & 0.4366 \\
2 & [0 1 1 0 0 1 1 1] & [0 0 1 0 1 0 1 1] & 50 & 0.4821 \\
 & [0 1 1 0 0 1 1 1] & [0 0 1 0 1 0 1 1] & 100 & 0.4911 \\
\hline
 & [1 0 1 1 1 1 1 1] & [0 1 1 0 0 1 1 0] & 10 & 0.3985 \\
3 & [1 0 1 1 1 1 1 1] & [0 1 1 0 0 1 1 0] & 50 & 0.3672 \\
 & [1 0 1 1 1 1 1 1] & [0 1 1 0 0 1 1 0] & 100 & 0.3725 \\
\hline
 & [1 0 1 1 1 1 0 1] & [1 1 0 1 0 1 0 0] & 10 & 0.4786 \\
4 & [1 0 1 1 1 1 0 1] & [1 1 0 1 0 1 0 0] & 50 & 0.4332 \\
 & [1 0 1 1 1 1 0 1] & [1 1 0 1 0 1 0 0] & 100 & 0.4189 \\
\hline
 & [1 0 0 1 1 0 0 0] & [0 1 0 1 0 1 1 0] & 10 & 0.6444 \\
5 & [1 0 0 1 1 0 0 0] & [0 1 0 1 0 1 1 0] & 50 & 0.5842 \\
 & [1 0 0 1 1 0 0 0] & [0 1 0 1 0 1 1 0] & 100 & 0.6179 \\
\hline
 & [1 0 0 1 1 0 0 0] & [1 1 1 1 0 0 0 0] & 10 & 0.4615 \\
6 & [1 0 0 1 1 0 0 0] & [1 1 1 1 0 0 0 0] & 50 & 0.4311 \\
 & [1 0 0 1 1 0 0 0] & [1 1 1 1 0 0 0 0] & 100 & 0.4872 \\
\hline
 & [0 0 1 0 1 1 1 0] & [0 1 0 0 0 0 0 1] & 10 & 0.5895 \\
7 & [0 0 1 0 1 1 1 0] & [0 1 0 0 0 0 0 1] & 50 & 0.6294 \\
 & [0 0 1 0 1 1 1 0] & [0 1 0 0 0 0 0 1] & 100 & 0.5574 \\
\hline
 & [0 0 1 1 0 1 0 1] & [1 1 1 0 0 1 1 0] & 10 & 0.4689 \\
8 & [0 0 1 1 0 1 0 1] & [1 1 1 0 0 1 1 0] & 50 & 0.4355 \\
 & [0 0 1 1 0 1 0 1] & [1 1 1 0 0 1 1 0] & 100 & 0.4476 \\
\hline
 & [0 0 0 0 0 1 1 0] & [1 0 1 1 1 1 0 1] & 10 & 0.5610 \\
9 & [0 0 0 0 0 1 1 0] & [1 0 1 1 1 1 0 1] & 50 & 0.5812 \\
 & [0 0 0 0 0 1 1 0] & [1 0 1 1 1 1 0 1] & 100 & 0.4877 \\
\hline
 & [0 1 1 1 0 0 0 0] & [1 1 1 1 1 0 0 1] & 10  & 0.4919 \\
10 & [0 1 1 1 0 0 0 0] & [1 1 1 1 1 0 0 1] & 50  & 0.4682 \\
 & [0 1 1 1 0 0 0 0] & [1 1 1 1 1 0 0 1] & 100  & 0.4158 \\
\hline
\end{tabular}
}
\end{table*}
